\documentclass[a4paper,11pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{tikz}
\usepackage{geometry}
\usepackage{listings}
\usepackage{xcolor}
\usepackage{hyperref}
\usepackage{enumitem}

\geometry{margin=1in}
\usetikzlibrary{shapes.geometric, arrows, positioning, shadow}

% Color Definitions
\definecolor{primaryBlue}{HTML}{1E3A8A}
\definecolor{secondaryGreen}{HTML}{22C55E}
\definecolor{surfaceLavender}{HTML}{FAF8FF}
\definecolor{alertSalmon}{HTML}{FEE2E2}
\definecolor{codeGray}{rgb}{0.95,0.95,0.95}

% TikZ Styles
\tikzstyle{startstop} = [rectangle, rounded corners, minimum width=3cm, minimum height=1cm,text centered, draw=black, fill=blue!10, drop shadow]
\tikzstyle{process} = [rectangle, minimum width=3cm, minimum height=1cm, text centered, draw=black, fill=orange!10, drop shadow]
\tikzstyle{decision} = [diamond, aspect=2, minimum width=3cm, minimum height=1cm, text centered, draw=black, fill=green!10, drop shadow]
\tikzstyle{arrow} = [thick,->,>=stealth, color=primaryBlue]

% Code Listing Style
\lstset{
    backgroundcolor=\color{codeGray},
    basicstyle=\ttfamily\small,
    breaklines=true,
    captionpos=b,
    commentstyle=\color{gray},
    keywordstyle=\color{primaryBlue},
    stringstyle=\color{secondaryGreen},
    frame=single
}

\begin{document}

% --- Title Page ---
\begin{titlepage}
   \centering
   \vspace*{2cm}
   \Huge \textbf{Bihari Kirana Digital Alien}\\
   \vspace{0.5cm}
   \Large Technical Specification \& Workflow Manual\\
   \vspace{1.5cm}
   \line(1,0){400}\\
   \vspace{1cm}
   \large \textbf{Project:} Inventory Management \& POS for Retail\\
   \textbf{Focus:} Efficiency, Bilingual Support, \& Profit Analytics\\
   \vfill
   \line(1,0){400}\\
   \medskip
   \small Created for BIHARI\_KIRANA Operations
\end{titlepage}

\tableofcontents
\newpage

% --- Section 1: Product Flow ---
\section{Product Lifecycle Flow (सामान का चक्र)}
This flowchart describes the physical and digital journey of an item within the store ecosystem.

\begin{center}
\begin{tikzpicture}[node distance=2cm]
\node (start) [startstop] {Stock Arrival (आवक)};
\node (reg) [process, below of=start] {Digital Registration};
\node (shelf) [process, below of=reg] {Inventory Active};
\node (monitor) [decision, below of=shelf, yshift=-0.5cm] {Sale Occurs?};
\node (update) [process, right of=monitor, xshift=3.5cm] {Stock Decrement};
\node (lowstock) [decision, below of=monitor, yshift=-1cm] {Below Min Limit?};
\node (restock) [process, left of=lowstock, xshift=-3.5cm] {Procurement};

\draw [arrow] (start) -- (reg);
\draw [arrow] (reg) -- (shelf);
\draw [arrow] (shelf) -- (monitor);
\draw [arrow] (monitor) -- node[anchor=south] {Yes} (update);
\draw [arrow] (update) |- (lowstock);
\draw [arrow] (monitor) -- node[anchor=east] {No} (lowstock);
\draw [arrow] (lowstock) -- node[anchor=south] {Yes} (restock);
\draw [arrow] (restock) |- (start);
\draw [arrow] (lowstock) -- node[anchor=east] {No} ++(0,-1.5) -| (shelf);
\end{tikzpicture}
\end{center}

% --- Section 2: Earning Flow ---
\section{Earning \& Financial Flow (कमाई का चक्र)}
How the system tracks every rupee from checkout to net profit.

\begin{center}
\begin{tikzpicture}[node distance=2.2cm]
\node (sale) [startstop] {POS Transaction};
\node (revenue) [process, below of=sale] {Gross Revenue (Cash/UPI)};
\node (purchase) [process, below of=revenue] {Deduct Unit Cost (COGS)};
\node (gross) [process, right of=purchase, xshift=3.5cm] {Gross Profit};
\node (expense) [process, below of=purchase] {Deduct Op-Expenses};
\node (net) [startstop, below of=expense, fill=green!20] {Net Profit (कमाई)};

\draw [arrow] (sale) -- (revenue);
\draw [arrow] (revenue) -- (purchase);
\draw [arrow] (purchase) -- (gross);
\draw [arrow] (purchase) -- (expense);
\draw [arrow] (expense) -- (net);
\end{tikzpicture}
\end{center}

\newpage

% --- Section 3: Technical Stack ---
\section{Technical Architecture}
The system is built for high availability and low latency in a retail environment.

\subsection{Tech Stack Details}
\begin{itemize}[label=$\bullet$]
    \item \textbf{Frontend:} Next.js 15 (App Router) with TypeScript for type-safe components.
    \item \textbf{Backend:} Supabase (PostgreSQL) for real-time inventory updates.
    \item \textbf{Styling:} Tailwind CSS 3.4 for a responsive, mobile-first retail UI.
    \item \textbf{State Management:} Zustand for fast, lightweight cart management.
    \item \textbf{Internationalization:} i18next for Bilingual (English/Hindi) support.
\end{itemize}

\subsection{Database Schema (SQL)}
The core logic relies on the following relational structure:
\begin{lstlisting}[language=SQL]
CREATE TABLE products (
  id UUID PRIMARY KEY DEFAULT uuid_generate_v4(),
  name TEXT NOT NULL,
  name_hi TEXT,
  purchase_price DECIMAL(10,2),
  selling_price DECIMAL(10,2),
  current_stock INTEGER,
  min_stock_alert INTEGER DEFAULT 5,
  expiry_date DATE
);
\end{lstlisting}

% --- Section 4: Operational Logic ---
\section{Business Intelligence Logic}

\subsection{Profit Calculation}
The system calculates real-time margins in the \texttt{Add/Edit Product} screens:
\begin{equation}
Profit\_Per\_Unit = Selling\_Price - Purchase\_Price
\end{equation}
\begin{equation}
Margin\% = \left( \frac{Profit\_Per\_Unit}{Purchase\_Price} \right) \times 100
\end{equation}

\subsection{Alert Thresholds}
\begin{enumerate}
    \item \textbf{Low Stock:} Triggered when $Current\_Stock \leq Min\_Stock\_Alert$.
    \item \textbf{Expiry Alert:} Highlighted if $Today > (Expiry\_Date - 7\,days)$.
\end{enumerate}

\section{Setup Instructions}
To run the system locally:
\begin{enumerate}
    \item Copy \texttt{example.env} to \texttt{.env} in the \texttt{web/} directory.
    \item Populate \texttt{NEXT_PUBLIC_SUPABASE_URL} and \texttt{NEXT_PUBLIC_SUPABASE_ANON_KEY}.
    \item Run \texttt{npm install} followed by \texttt{npm run dev}.
\end{enumerate}

\end{document}
